Re-visiting the Political Deepfake Videos Misinformation the Public But No More than Other Fake Media (2021)

### 2021-03-24 outputs/paper/Paper3_Output.Rmd
fixing heading

##Detection experiment results
```{r fig03, fig.cap='Marginal Means in Detection Experiment Outcomes',echo = FALSE, warning=FALSE, fig.align = "center", regfloat=TRUE}
knitr::include_graphics(here::here("figures/topline_exp2.pdf"))
```

>>>>

## Detection experiment results
```{r fig03, fig.cap='Marginal Means in Detection Experiment Outcomes',echo = FALSE, warning=FALSE, fig.align = "center", regfloat=TRUE}
knitr::include_graphics(here::here("figures/topline_exp2.pdf"))
```
